Something about Performance, 2D Component of NEMO. (TBC)

### 2015-05-05 docs/papers/nemolite2d_performance/nemolite2d_perf.tex
Add Mike to author list. Add plots of OMP performance for 32x32 domain.

\author{J.~Appleyard, R.~W.~Ford, J.~Holt, H.~Lieu, A.~R.~Porter and G.~D.~Riley% <-this % stops a space
\thanks{J.~Appleyard is with NVIDIA.}%
\thanks{H.~Lieu and J.~Holt are with the National Oceanography Centre, Liverpool, UK.}%
\thanks{A.~R.~Porter and R.~Ford are with the Science and Technology Facilities Council, UK.}% <-this % stops a space
\thanks{G.~Riley is with the University of Manchester, Manchester, UK.}% <-this % stops a space
}

@@

>>>>

\author{J.~Appleyard, M.~Ashworth, R.~W.~Ford, J.~Holt, H.~Lieu, A.~R.~Porter and G.~D.~Riley% <-this % stops a space
\thanks{J.~Appleyard is with NVIDIA.}%
\thanks{H.~Lieu and J.~Holt are with the National Oceanography Centre, Liverpool, UK.}%
\thanks{M.~Ashworth, R.~W.~Ford and A.~R.~Porter are with the Science and Technology Facilities Council, UK.}% <-this % stops a space
\thanks{G.~Riley is with the University of Manchester, Manchester, UK.}% <-this % stops a space
}

@@

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_32_gnu}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Gnu compiler on a single Intel Ivy Bridge
  socket. The corresponding parallel efficiencies are shown using open
  symbols and dashed lines. The 24-thread runs employed hyperthreading
  and the optimal OpenMP schedule is given in parentheses.}
\label{FIG_gnu_omp_32}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_32_intel}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Intel compiler on a single Intel Ivy Bridge
  socket.  The corresponding parallel efficiencies are shown using
  open symbols and dashed lines. The 24-thread runs employed
  hyperthreading and the optimal OpenMP schedule is given in
  parentheses.}
\label{FIG_intel_omp_32}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\picwidth]{omp_scaling_32_cray}
\caption{Performance of the OpenMP-parallel version of \psykal
  nemolite2d for the Cray compiler on a single Intel Ivy Bridge
  socket.  The corresponding parallel efficiencies are shown using
  open symbols and dashed lines. The 24-thread runs employed
  hyperthreading and the optimal OpenMP schedule is given in
  parentheses.}
\label{FIG_cray_omp_32}
\end{figure}
